### 2018-09-12 chapter-latex/abstract.tex
added the springer chapter latex --post-review --post-response-to-review --pre-send-to-editor

\documentclass[graybox,envcountchap,sectrefs%
,footinfo
%,referee
]{svmono}
% Native packages
\usepackage{mathptmx}
\usepackage{helvet}
\usepackage{courier}
\usepackage{type1cm}         
\usepackage{makeidx}		% allows index generation
\usepackage{graphicx}		% standard LaTeX graphics tool
\usepackage{multicol} 		% used for the two-column index
\usepackage[bottom]{footmisc}	% places footnotes at page bottom
% User packages
\usepackage{natbib}
\usepackage{lipsum}
\usepackage{placeins}
\makeindex             			% used for the subject index
                       				% please use the style svind.ist with
                       				% your makeindex program

\begin{document}

\author{Kees van Deemter and Matthew Green}
\title{Vagueness \& Rationality}
\subtitle{The Elusive Benefits of Vagueness: the Evidence So Far}
\maketitle

\frontmatter
\tableofcontents

\mainmatter%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

Your text goes here.

\chapter{Chapter Heading}
\label{intro1} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head

Your text goes here. Separate text sections with the standard \LaTeX\
sectioning commands.

\section{Section Heading}
\label{sec:1.1}
% Always give a unique label
% and use \ref{<label>} for cross-references
% and \cite{<label>} for bibliographic references
% use \sectionmark{}
% to alter or adjust the section heading in the running head
Your text goes here. Use the \LaTeX\ automatism for your citations
\cite{vanDeemterCMR}.

\subsection{Subsection Heading}
\label{sec:2}
Your text goes here.

\begin{equation}
\vec{a}\times\vec{b}=\vec{c}
\end{equation}

\subsubsection{Subsubsection Heading}
Your text goes here. Use the \LaTeX\ automatism for cross-references as
well as for your citations, see Sect.~\ref{sec:1}.

\paragraph{Paragraph Heading} %
Your text goes here.

\subparagraph{Subparagraph Heading.} Your text goes here.%
%
\index{paragraph}
% Use the \index{} command to code your index words
%
% For tables use
%
\begin{table}
\centering
\caption{Please write your table caption here}
\label{tab:1}       % Give a unique label
%
% For LaTeX tables use
%
\begin{tabular}{lll}
\hline\noalign{\smallskip}
first & second & third  \\
\noalign{\smallskip}\hline\noalign{\smallskip}
number & number & number \\
number & number & number \\
\noalign{\smallskip}\hline
\end{tabular}
\end{table}
%
%
% For figures use
%
\begin{figure}
\centering
% Use the relevant command for your figure-insertion program
% to insert the figure file.
% For example, with the option graphics use
%\includegraphics[height=4cm]{figure.eps}
%
% If not, use
%\picplace{5cm}{2cm} % Give the correct figure height and width in cm
%
\caption{Please write your figure caption here}
\label{fig:1}       % Give a unique label
\end{figure}
%
% For built-in environments use
%
\begin{theorem}
Theorem text goes here.
\end{theorem}
%
% or
%
\begin{lemma}
Lemma text goes here.
\end{lemma}
%
%
% Problems or Exercises should be sorted chapterwise
\section*{Problems}
\addcontentsline{toc}{section}{Problems}
%
% Use the following environment.
% Don't forget to label each problem;
% the label is needed for the solutions' environment
\begin{prob}
\label{prob1}
The problem\footnote{Footnote} is described here. The
problem is described here. The problem is described here.
\end{prob}

\begin{prob}
\label{prob2}
\textbf{Problem Heading}\\
(a) The first part of the problem is described here.\\
(b) The second part of the problem is described here.
\end{prob}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% our chapter START
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{The Elusive Benefits of Vagueness: Evidence from Experiments}
\label{intro} % Always give a unique label
% use \chaptermark{}
% to alter or adjust the chapter heading in the running head

Much of everyday language is vague, even in situations where vagueness could have been
avoided (i.e., where vagueness is used “strategically"). Yet the benefits of vagueness for
hearers and readers are proving to be elusive. We discuss a range of earlier controlled
experiments with human participants, and we report on a new series of experiments that
we conducted in recent years. These experiments, which focus on vague expressions that
are part of referential noun phrases, aim to separate the utility of vagueness (as defined by
the existence of borderline cases) from the utility of other factors that tend to co-occur
with vagueness. Having presented the evidence, we argue that the evidence supports a view
where the benefits that vague terms exert are due to other influences, and not to vagueness
itself.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% our chapter END
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\backmatter%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% BibTeX users please use
\bibliographystyle{spbasic} %plain, harvard, apalike, chicago, astron, authordate, natbib.
\bibliography{v-book}

\backmatter

\printindex
\end{document}

>>>>

Much of everyday language is vague, even in situations where vagueness could have been avoided (i.e., where vagueness is used ``strategically''). Yet the benefits of vagueness for hearers and readers are proving to be elusive. We discuss a range of earlier controlled experiments with human participants, and we report on a new series of experiments that we conducted in recent years. These experiments, which focus on vague expressions that are part of referential noun phrases, aim to separate the utility of vagueness (as defined by the existence of borderline cases) from the utility of other factors that tend to co-occur with vagueness. Having presented the evidence, we argue that the evidence supports a view where the benefits that vague terms exert are due to other influences, and not to vagueness itself.

### 2018-09-12 chapter-latex/e1.tex
added the springer chapter latex --post-review --post-response-to-review --pre-send-to-editor

\begin{itemize}
	\item In the vague numerical condition the instruction was "Choose a square with about 10 dots" -- none of the arrays contained exactly 10 dots, but 10 is closer to 6 than it is to 15, making 6 a better response to that instruction, 15 a borderline response, and 24 an extreme response. 
	\item In the vague verbal condition we used "Choose a square with few dots". We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
	\item In the crisp numerical condition we used "Choose the square with 6 dots". The smaller flanking array always contained exactly the specified number of dots. We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
	\item For crisp verbal, we used "Choose the square with the fewest dots". We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
\end{itemize}

On each trial, first the referring expression that constituted the instruction for that trial was displayed (e.g., "Choose a square with about 10 dots"). Participants then pressed a key to indicate that they had read the instruction. The instruction remained on screen, and after 1000 ms, the arrays appeared. An example stimulus is given in Figure \ref{Experiment1and2examplestimulus}. Response time was measured from the presentation of the arrays until the keypress indicating the participant's choice. The trial would timeout after 60 seconds if there was no response. In this experiment, no feedback was given. This was because, in the vague conditions, we did not regard any response as "correct" or "incorrect", but instead as "expected response"; "borderline response"; and "extreme response", and we did not want to draw participants' attention to this distinction explicitly. Which choice the participant made was recorded for analysis.

>>>>

\begin{itemize}
	\item In the vague numerical condition the instruction was ``Choose a square with about 10 dots" -- none of the arrays contained exactly 10 dots, but 10 is closer to 6 than it is to 15, making 6 a better response to that instruction, 15 a borderline response, and 24 an extreme response. 
	\item In the vague verbal condition we used ``Choose a square with few dots". We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
	\item In the crisp numerical condition we used ``Choose the square with 6 dots". The smaller flanking array always contained exactly the specified number of dots. We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
	\item For crisp verbal, we used ``Choose the square with the fewest dots". We considered this to be equivalent in terms of which responses were expected (6), borderline (15) and extreme (24).
\end{itemize}

On each trial, first the referring expression that constituted the instruction for that trial was displayed (e.g., ``Choose a square with about 10 dots"). Participants then pressed a key to indicate that they had read the instruction. The instruction remained on screen, and after 1000 ms, the arrays appeared. An example stimulus is given in Figure \ref{Experiment1and2examplestimulus}. Response time was measured from the presentation of the arrays until the keypress indicating the participant's choice. The trial would timeout after 60 seconds if there was no response. In this experiment, no feedback was given. This was because, in the vague conditions, we did not regard any response as ``correct" or ``incorrect", but instead as ``expected response"; ``borderline response"; and ``extreme response", and we did not want to draw participants' attention to this distinction explicitly. Which choice the participant made was recorded for analysis.

### 2018-09-12 chapter-latex/general-discussion.tex
added the springer chapter latex --post-review --post-response-to-review --pre-send-to-editor

A comparison may clarify the logic of the situation. In recent years a number of studies, focussing on red wine, have suggested that alcohol, consumed in low doses, may have health benefits. An alternative explanation, however, asserts that it is not the alcohol in the wine that was beneficial, but antioxidants from grapes. If this alternative explanation is correct, then alcohol may not be healthy after all.\\[2ex]
%
% KvD Feb 2017. I've diminished the role of NLG in the coming paragraph.
Our findings suggest a re-think of the questions on which much research on the utility of vagueness rests. Years of research on the logic of vagueness -- giving rise to such techniques as Partial Logic \citep[e.g.,]{Fine}, Probabilistic Logic \citep{Edgington}, and Fuzzy Logic \citep{Zadeh} -- have primed the research community to expect that some special utility of vagueness is an important part of the answer, but our findings call this expectation into question.

@@

First, the experiments by \citeauthor{Mishra01042011} suggest that it is important how much information is conveyed by an expression, and their findings are echoed by our own thoughts about range reduction (following Experiments 2 and 3). In the case of (a)--(d) above, it appears that (a) conveys the most detailed information (designating the smallest segment of the temperature scale), followed by (b), then (d), then (c) (e.g., 40 degrees is above 25, but at 40 Celsius the word ``warm'' is likely to give way to ``hot'' or ``scorching''): 
%
\begin{quote}
$a < b < d < c$
\end{quote}
%
If these hunches are correct, then it seems to us that it is relatively unimportant whether a given expression is vague or crisp. Other factors seem more important; moreover, it may depend on the task and the audience which of a-d is preferred. For example, an \emph{expert} may prefer to read expression (a), because it gives her the most detailed information on which to base her decisions. On the other hand, expression (d) (``warm'') is shorter than the other three and avoids the use of numbers; our experiments suggest that this may make (d) more rapidly understood than its competitors; earlier experiments point in the same direction, given the evaluative nature of ``warm'' (see our section 1 and  \citeauthor{peters2009bringing}), which is especially important if the hearer is unfamiliar with the metric used. These considerations suggest that {\em non-experts} might prefer expression (d).

>>>>

A comparison may clarify the logic of the situation. In recent years a number of studies, focussing on red wine, have suggested that alcohol, consumed in low doses, may have health benefits. An alternative explanation, however, asserts that it is not the alcohol in the wine that was beneficial, but antioxidants from grapes. If this alternative explanation is correct, then alcohol may not be healthy after all.\\[2ex]
%
% KvD Feb 2017. I've diminished the role of NLG in the coming paragraph.
Our findings suggest a re-think of the questions on which much research on the utility of vagueness rests. Years of research on the logic of vagueness -- giving rise to such techniques as Partial Logic \citep[e.g.,][]{Fine}, Probabilistic Logic \citep{Edgington}, and Fuzzy Logic \citep{Zadeh} -- have primed the research community to expect that some special utility of vagueness is an important part of the answer, but our findings call this expectation into question.

@@

First, the experiments by \citeauthor{Mishra01042011} suggest that it is important how much information is conveyed by an expression, and their findings are echoed by our own thoughts about range reduction (following Experiments 2 and 3). In the case of (a)--(d) above, it appears that (a) conveys the most detailed information (designating the smallest segment of the temperature scale), followed by (b), then (d), then (c) (e.g., 40 degrees is above 25, but at 40 Celsius the word ``warm'' is likely to give way to ``hot'' or ``scorching''): 
%
\begin{quote}
$a < b < d < c$
\end{quote}
%
If these hunches are correct, then it seems to us that it is relatively unimportant whether a given expression is vague or crisp. Other factors seem more important; moreover, it may depend on the task and the audience which of a-d is preferred. For example, an \emph{expert} may prefer to read expression (a), because it gives her the most detailed information on which to base her decisions. On the other hand, expression (d) (``warm'') is shorter than the other three and avoids the use of numbers; our experiments suggest that this may make (d) more rapidly understood than its competitors; earlier experiments point in the same direction, given the evaluative nature of ``warm'' (recall our section 1.2), which is especially important if the hearer is unfamiliar with the metric used. These considerations suggest that {\em non-experts} might prefer expression (d).
